Pothole is a common problem in roads and streets. Vehicles get damaged, people get stumbled. This may cause physical injury to humans. Moreover, visually impaired people suffer much due to potholes. Therefore, they have to be detected and avoided on the way. But currently available systems are not suitable for blind-persons, although some of them are capable of helping vehicle-drivers to get aware of the potholes in front of them. Many of the systems lack exact localization of potholes, some are location dependent. Here, we represent a robust, cost-effective solution to the problem of pothole detection and localization. Our proposed system is capable of detecting potholes in real-time, therefore useful for automatic car-driving. It processes the frames coming from a  video camera, uses a deep neural network (Single Shot Multibox Detector with MobileNet) for detection and fires an alarm instantly to notify about the detected potholes. We collected our dataset by web-scraping as well as camera shoting. Total 665 images are annotated with regions of interest as bounding boxes. Then we randomly split the dataset taking 80\% for training and 20\% for validation. Fine tuning the pre-trained model for our data-set, we trained it using TensorFlow Object Detection API. Finally we deployed our model to an android application to test detection in real-time. We got satisfactory results from the system. Despite having a small dataset our model performs well. In future, we will use larger dataset, try to measure the severity of the detected pothole and make it aware of ignorable potholes.
