\chapter{Conclusion and Future Works}
    In this chapter we are going to conclude our research work. Appearance of a brief overview about what to be done in future regarding this research is also shown in this chapter.
    
    \section{Conclusion}
        Although many research in the field of pothole detection have already taken place there are some limitations and problems with existing solutions. We have proposed a method for real-time pothole detection and localization as well as tracking the potholes in the video frames coming from a camera module. We have used 665 images annotated the regions of interest to prepare dataset. \acrfull{ssd} \gls{mobilenet}, a deep-convolutional neural network designed by Google-researchers for object detection was used as a pre-trained model. We have fine tuned the model with our dataset and used TensorFlow \acrshort{api} for this purpose. Finally, we deployed our model to an android application which is an out-of-the-box usable application for pothole detection and localization in real-time.
    
    \section{Future Works}
        Despite working and building a robust, fast, cost-effective model for pothole detection and localization in real-time, we realize that we need more research-work to make the proposed system more intelligent and error-free. Currently, like other technical systems, our proposed system also has some limitations and drawbacks. In future, we will try to solve the problems.
        
        Our model was trained using a small dataset which is a drawback because, the more data we train on, the more accurate the model would be.
        
        \subsection{Use Larger Dataset}
            In future, we will collect and prepare a larger dataset to train our model. This will make our detector model more robust, more accurate, more error-free and more intelligent.
            
        \subsection{Measure the Depth of Pothole}
            Our current proposed system cannot measure how deep the detected pothole is. This is an important feature though. We will try to implement this feature in future.
            
        \subsection{Calculate the Area of Pothole}
            Currently, our proposed system is not configured to measure the area of the detected potholes. This will be very helpful if implemented.
            We will try to do it in near future.
            
        \subsection{Measure the Severity of Pothole}
            Measuring the severity of the detected pothole is an important task. Our currently proposed model cannot do that. We will implement this strategy in upcoming days. 
            
%         \subsection{Identify Safe Direction}
%             It will be a great advancement if it could be determined which direction does not have any pothole or possibly safe to move through.
%             We have an idea to implement this feature in the near future.
